---
title: "correspondence_price_rights"
output:
  html_document: default
  pdf_document: default
date: "2025-04-27"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Correspondence between transfers in a cap-and-trade and differentiated carbon prices

<!--

format:
  latex:
    keep-tex: true
    -->
## The static case
### Setting

Decarbonization is costly. When a country $i$ faces a carbon price $p_i$, it curtails consumption by investing in low-carbon equipment and reorienting consumption to less preferred, less carbon-intensive products. These costs to consumption are called abatements costs and denoted $a_i$. Taking into account the possibility of transfers $t_i$ from the rest of the world, expressing everything in per capita terms, abstracting from exogenous investments, country i's consumption is related to its potential output $y_i$ as follows: $$c_i = y_i + t_i - a_i(p_i)$$

Assume that the welfare of country $i$ depends on its consumption $c_i$ and global emissions $E=\sum_j e_j n_j$, where $e_j$ is country's $j$  per capita emissions and $n_j$ its population size. For now, take global emissions as fixed at their optimal level $E^*$. Let $p^*$ be the uniform carbon price required to attain $E^*$, i.e. $E^*=\sum_j e_j(p^*) n_j$.

**A situation is fully specified by the set of transfers $(t_j)_j$ and carbon prices $(p_j)_j$ for each country**. For country $i$, given that global emissions are taken as fixed, the situation can be summarized as $s=(t_i, p_i)$, and (with a slight abuse of notation) we may express $i$'s welfare accordingly: $u_i(c_i;E^*)=u_i(t_i,p_i)$. 


### Equivalent variation from the benchmark in the absence of transfers

To analyze an arbitrary situation $s$, it will be useful to relate it to two special cases. First, the coordinated situation $c*=(0,p^*)$, without transfer and with a uniform carbon price, which we take as a benchmark. Second, the autarchy situation $a=(0, p_i)$, without transfer and with differentiated prices, which will be a useful intermediary to analyze an arbitrary situation. We denote $V_i(p_i)$ the equivalent variation between situation $a$ and $c*$, i.e. the transfer required at $c*$ to get $a$'s welfare:
$$\begin{aligned}
u_i(V_i(p_i), p^*)&=u^a_i=u_i(0, p_i) \\
c^{c*}_i + V_i(p_i) &= c^a_i
\end{aligned}$$
In terms of welfare:
$$\begin{aligned}
u_i(V_i(p_i), p^*)&=u^a_i=u_i(0, p_i)=u_i(y_i-a_i(p_i))\sim u^{c*}_i - (p_i - p^*) \partial a_i \partial u_{i1} \\
u_i(V_i(p_i), p^*)&= u^{c*}_i + V_i(p_i)\partial u_{i1}
\end{aligned}$$

where **$\partial a_i$ is the marginal abatement cost at $p^*$**.
Therefore, at the first order,
$$V_i(p_i) = (p^* - p_i) \partial a_i$$

$V_i$ is positive iff $p^* > p_i$ as country i ``needs'' a positive compensation for consumption to get the same welfare as in (a) with a higher price $p^*$ (and lower emissions) compared to $c*$.

<!--
### Optimality of the uniform price TODO? I don't find a simple derivation

At the second order, $i$'s equivalent variation between $a$ and $c*$ is: $$V_i(p_i) = (p^* - p_i) \partial a_i + \frac{1}{2} (p^* - p_i)^2 (\partial^2 u_{i1} (\partial a_i)^2 - \partial u_{i1} \partial^2 a_i)$$

If we assign the same welfare weight to every country, the world welfare is the average of countries' welfare weighted by their population size. The world welfare in any autarchy situation can then be compared to the world welfare in the coordinated situation by looking at the average equivalent variation (weighted by population size): $\overline{V}=\sum_j V_j(p_j) n_j$. 
If $p^*$ is the average price, they the first order term vanish. TODO: Pb: why would that be the case?
If $a_i$ are all convex and $u_i$ concave, the second-order terms are all negative, so autarchy is welfare inferior.
-->

### Equivalent transfer for an arbitrary situation

Let $g^s_i$ be country $i$'s net gain (or ``equivalent transfer'') in an arbitrary situation $s=(t_i, p_i)$ compared to the benchmark situation $c*=(0,p^*)$: 
$$\begin{aligned}
g^s_i &= (c^s_i - c^a_i) + (c^a_i - c^{c*}_i) \\
 &= t_i + V_i(p_i)
\end{aligned}$$
Note that **we can call $g^s_i$ the equivalent transfer as it is the transfer at zero price that makes $i$ indifferent with $s$, i.e. the transfer such that $(g^s_i, 0)$ is welfare-equivalent to $s=(t_i, p_i)$**. The equivalent transfer is a very useful metric to compare the welfare of a country in different situations.


### Correspondence with an equivalent price

Now, we have all the tools to study the correspondence between transfers, differentiated emission rights, and differentiated prices. 
Let $p^*_i$ be the ``equivalent price'' such that $s=(t_i, p_i)$ is welfare-equivalent to $s*=(0, p^*_i)$. 
$$\begin{aligned}
g^s_i &= g^{s*}_i \\
t_i + V_i(p_i) &= V_i(p^*_i) \\
t_i + (p^* - p_i) \partial a_i &= (p^*- p^*_i) \partial a_i \\
\end{aligned}$$

Therefore, the equivalent price is:
$$p^*_i = p_i - \frac{t_i}{\partial a_i} $$

The equivalent price is negative when $p_i \partial a_i < t_i$. As a negative price would require a transfer from the rest of the world, a regime with differentiated (positive) prices is restrictive compared to a system that allows for international transfers. <!-- To implement transfers in the case where the equivalent price would be negative, -->
Therefore, **we prefer to use the concept of equivalent transfer $g^s_i$, rather than its dual the equivalent price**. From the above, the equivalent transfer can be expressed as:

$$g^s_i = t_i + (p^* - p_i) \partial a_i$$


### Correspondence between differentiated prices and rights

<!-- Denote $p$ the world average carbon price: $p=\sum_j p_j e_j n_j / E$, and $e$ the world average emission: $e=\sum_j e_j n_j / \sum_j n_j$.

Let us consider the case where countries pool their carbon price revenue: they collectively collect $\sum_j e_j p_j n_j = Ep$. -->
Imagine that countries establish a uniform carbon price $p^*$, e.g. through a cap-and-trade. Say each person in country $i$ has an emission right $r_i$, so they are entitled a claim $r_i p^*$ on global carbon revenue. Therefore, the net monetary transfer to $i$ is $$t^*_i = r_i p^* - e^*_i p^*$$

In the static case, **there is a correspondence between emission rights $r_i$ in a cap-and-trade and differentiated prices $p_i$ in autarchy (without transfers)**: 
$$\begin{aligned}
g^a_i &= V_i(p_i) = (p^* - p_i) \partial a_i \\
g^*_i &= t^*_i = (r_i - e^*_i) p^* \\
g^*_i = g^a_i &\Leftrightarrow (r_i - e^*_i) p^* = (p^* - p_i) \partial a_i
\end{aligned}$$

The left-hand side is the cap-and-trade equivalent transfer, which corresponds to the net monetary transfer received in the uniform cap-and-trade. The equivalence relation states that it is negatively related to the difference between the autarchy price and the global cap-and-trade price. The coefficient of this linear relation is the marginal abatement cost: the costlier abatement is, the larger the effect of the autarchy carbon price on the cap-and-trade equivalent transfer. 

One can easily isolate cap-and-trade emission rights or autarchy price in function of the other variables:
$$\begin{aligned}
g^*_i = g^a_i &\Leftrightarrow r_i = e_i^* + (1 - \frac{p_i}{p^*}) \partial a_i  \\
&\Leftrightarrow p_i = p^* (1 + \frac{e^*_i - r_i}{\partial a_i})
\end{aligned}$$

<!--
TODO: estimate $\partial a_i$

Let us compare two special cases: a situation $d$ with differentiated prices but equal rights: $d=(ep-e_i p_i, p_i)$, and a situation $u$ with a uniform price but differentiated rights: $u=(r_i p^* - e_i p^*, p^*)$. We have:

$$\begin{aligned}
g^d_i &= ep - e_i p_i + V_i(p_i) \\
g^u_i &= r_i p^* - e_i p^*  \\
g^u_i - g^d_i &= r_i p^* - ep + (p_i - p^*) (e_i + \partial a_i) 
\end{aligned}$$
-->

### Using the status quo as benchmark

If, instead of using $c*=(0, p^*)$ as the counterfactual, governments use the status quo $c^- = (0, p^-)$, with $p^-<p^*$. Then, the net gain they consider is 
$$\begin{aligned}
\gamma_i &= (y_i + t_i - a_i(p_i)) - (y_i - a_i(p^-)) + (E^* - E^-) \partial u_{i2}/\partial u_{i1} \\
 &= t_i -a_i(p_i) + a_i(p^-) + (E^* - E^-) \partial u_{i2}/\partial u_{i1} \\
 &\sim t_i + (p^- - p_i) \partial a_i + (p^* - p^-) \partial E \partial u_{i2}/\partial u_{i1} \\
 &= g_i - V_i(p^-) + (E^* - E^-) \partial u_{i2}/\partial u_{i1} \\
\end{aligned}$$ 
where $\partial u_{i2}$ corresponds to the welfare benefits of lower world emissions.

The gain relative to the status quo $\gamma_i$ is larger than the gain relative to $c*$ iff the price $p^*$ would improve welfare compared to the status quo price $p^-$, i.e. iff the welfare benefit from lower emissions exceeds the cost of decarbonization: 
$$\gamma_i > g_i \Leftrightarrow (E^* - E^-) \partial u_{i2}/\partial u_{i1} > V_i(p^-) $$


### Abatement cost required as transfer by those neglecting climate costs

From the point of view of short-sighted governments, we are likely in the other case $\gamma_i < g_i$, and these governments likely use $\gamma_i$ as a counterfactual to assess welfare. In the worst case where a government doesn't attach any value to a stable climate, accepting a price increase $\Delta p_i = p_i - p^-$ requires a transfer larger than the abatement costs:
$$t_i > V_i(p^-) = \Delta p_i \partial a_i$$

Conceptually, abatement costs can be divided in two parts: first, the extra investments needed to build and deploy low-carbon infrastructure; second, the curtailment of consumption (of energy, meat, flights...) entailed by a higher carbon price. The former can be estimated with a bottom-up energy model; the latter using the short (or medium) term price-elasticity of emissions $\epsilon = \frac{\partial e}{e}/\frac{\partial p}{p}$ and the crude approximation that emissions represent one-twentieth of the consumption (corresponding to about half the energy share). Assuming $\epsilon = .4$, the effect on consumption of an increase in price by a factor $\delta p$ is therefore: $\delta c = \frac{\partial c/c}{\partial e/e} \epsilon \delta p = .05 \cdot .4 \cdot \delta p = .02 \cdot \delta p$. So, as a first approximation, a doubling of the carbon price should be compensated with a transfer of at least 2% of GDP.


## The dynamic case

### Setting

In this section, we will show that the correspondence between transfers and differentiated carbon prices imperfectly extends to the dynamic case. 

Let us keep the previous notations and add an index $t$ to denote the value of a variable at time $t$. Let $\beta_t$ be the discount factor between the initial period and $t$ (containing the pure rate of time preference and the welfare discounting from growth). Intertemporal values are denoted with uppercase letters. Monetary variables are discounted while physical ones are not, e.g. <!-- the intertemporal consumption of $i$ is $C_i = \sum_t c_{it} \beta_t$, its -->
$i$'s intertemporal net gain is $G_i = \sum_t g_{it} \beta_t$ and its intertemporal emission right is $R_i = \sum_t r_{it}$.

A situation $S$ is now given by the transfers and prices trajectories: $S=((t_{it})_t, (p_{it})_t)$. Taking $y_{it}$ as exogenous as a first approximation, for country $i$ a situation $S$ is welfare-equivalent to a situation $S'$ with the same temperature trajectory iff: $\sum_t t_{it} - a_{it}(p_{it}) = \sum_t t'_{it} - a_{it}(p'_{it})$.


### The uniform price without transfer case as benchmark

<!-- Consider the situation $C*$ of a global cap-and-trade system with a uniform carbon price. The transfers and price trajectories are determined by the allocation of the global intertemporal carbon budget $B$ at the country-by-period level: $(r_{it})_t$. -->
Consider the situation $C*=(0,(p^*_t)_t)$ of a uniform carbon price trajectory $(p^*_t)_t$ and within-country revenue recycling (i.e. without transfers). The carbon price trajectory may be fixed in advance or emerge from the temporal allocation of the global intertemporal carbon budget (or emission right) $R$ in a cap-and-trade system: $(r_{t})_t$. Let us define the net gain for $i$ at $t$ in a situation $S$ (with the same emissions trajectory as $C*$) in relation to $C*$. As above: $g_{it} = t_{it} + V_{it}(p_{it})$, where $V_{it}(p_{it}) = (p^*_t - p_{it}) \partial a_{it}$.


### A more limited correspondence between differentiated prices and rights

As in the static case, let us look for a correspondence between an autarchy situation $A$ with differentiated prices and a cap-and-trade system $U$ with uniform price. In the general case, $A=(0, (p_{it})_t)$ while $U=((r_{it}p^*_t-e^*_{it}p^*_t)_t, (p^*_t)_t)$ is indirectly determined by $r=(r_{it})_t$. The welfare equivalence for $i$ between $A$ and $U$ can be derived as follows:
$$\begin{aligned}
G^A_i &= \sum_t (p^*_t - p_{it}) \partial a_{it} \beta_t \\
G^U_i &= \sum_t (r_{it} - e^*_{it}) p^*_t \beta_t \\
G^U_i = G^A_i &\Leftrightarrow \sum_t r_{it} \beta_t p^*_t  = \sum_t (\partial a_{it} + e^*_{it}) p^*_t \beta_t - \sum_t p_{it} \partial a_{it} \beta_t  
\end{aligned}$$

**Contrary to the static case, there is no direct equivalence between an intertemporal aggregate of the emission rights and an intertemporal aggregate of differentiated prices**, since the welfare effect of emission rights depends on the cap-and-trade price trajectory $p^*_t$. 

The same reason also complicates the comparison between two possible allocations $r$ and $r'$ of the intertemporal carbon budget in a cap-and-trade, even when the price trajectories coincide. Indeed, the condition $G^U_i > G^{U'}_i \Leftrightarrow \sum_t r_{it} \beta_t p^*_t > \sum_t r'_{it} \beta_t p^*_t$ does *not* imply that $R_i = \sum_t r_{it} > \sum_t r'_{it} = R'_i$. In other words, **there is no immediate relation between $i$'s intertemporal carbon budget and its intertemporal welfare, as the price trajectory matters**.

Let us study whether we can find a correspondence in simpler cases. For the autarchy situation $A$, consider a homothetic carbon price vis-à-vis the world average: $p_{it}=\pi_ip_t$. For the cap-and-trade situation $U$, consider that $i$ is granted a fixed share of the world's carbon budget: $r_{it}=r_ir_t$. Now, the equivalence between $A$ and $U$ rewrites:

$$\begin{aligned}
G^U_i = G^A_i &\Leftrightarrow r_i \sum_t r_{t} \beta_t p^*_t  = \sum_t (\partial a_{it} + e^*_{it}) p^*_t \beta_t - \pi_i \sum_t p_{t} \partial a_{it} \beta_t  
\end{aligned}$$

Provided that the price trajectories in autarchy are homothetic to the price trajectory in the cap-and-trade (without loss of generality): $p_{it}=\pi_ip^*_t$; the equivalence simplifies further:

$$G^U_i = G^A_i \Leftrightarrow r_i \mathscr{B} = \mathscr{E} + (1 - \pi_i) \mathscr{\partial A}$$
where $\mathscr{B} = \sum_t r_{t} \beta_t p^*_t$, $\mathscr{E} = \sum_t e^*_{it} p^*_t \beta_t$, and $\mathscr{\partial A} = \sum_t \partial a_{it} p^*_t \beta_t$.

**Although we do find a correspondence in this special case**, the formula faces practical limitations, as **it requires knowing the future price trajectory $(p^*_t)_t$, which can only be imprecisely estimated** in the cap-and-trade situation. In any case, although one can find a trajectory of differentiated prices welfare equivalent to a given allocation of emissions rights, and vice versa, the derivation cannot be done analytically, **one has to resort to an integrated assessment model**. 

However, **in the Hotelling case** (with a fixed carbon budget, perfect foresight, and efficient capital markets), the formula simplify further. Indeed, the Hotelling price grows at the discount rate, so that the discounted price is constant: $\beta_t p^*_t = p_0$. Only in this very special case, **the formula simplifies to a formula analogous to the static case one**:

$$G^U_i = G^A_i \Leftrightarrow R_i - E^*_i = (1 - \pi_i) \sum_t{\partial a_{it}}$$
<!--
$$\begin{aligned}
G^U_i = G^A_i &\Leftrightarrow R_i = E_i + (1 - \pi_i) \sum_t{\partial a_{it}} \\
&\Leftrightarrow \pi_i = 1 + \frac{E_i - r_i R}{\sum_t{\partial a_{it}}}
\end{aligned}$$
-->

<!-- https://bsky.app/profile/did:plc:2b4tsqp7a47hhyk3weki7epo/post/3lydrek33fc2x -->


```{r, echo=FALSE}



```
