---
title: "correspondence_price_rights"
output:
  html_document: default
  pdf_document: default
date: "2025-04-27"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Correspondence between transfers in a cap-and-trade and differentiated carbon prices

## The static case
### Setting
TODO: replace b by r and r by beta

Decarbonization is costly. When country $i$ faces a carbon price $p_i$, it curtails consumption by investing in low-carbon equipment and reorienting consumption to less preferred, less carbon-intensive products. These costs to consumption are called abatements costs and denoted $a_i$. Taking into account the possibility of transfers $t_i$ from the rest of the world, expressing everything in per capita terms, and abstracting from exogenous investments, country i's consumption is related to its potential output $y_i$ as follows: $$c_i = y_i + t_i - a_i(p_i)$$

Assume that welfare of country $i$ depends on its consumption $c_i$ and global emissions $E=\sum_j e_j n_j$, where $e_j$ is country's $j$  per capita emissions and $n_j$ its population size. For now, take global emissions as fixed at their optimal level $E^*$. Let $p^*$ be the uniform carbon price required to attain $E^*$, i.e. $E^*=\sum_j e_j(p^*) n_j$.

A situation is fully specified by the set of transfers $(t_j)_j$ and carbon prices $(p_j)_j$ for each country. For country $i$, given that global emissions are taken as fixed, the situation can be summarized as $s=(t_i, p_i)$, and (with a slight abuse of notation) we may express $i$'s welfare accordingly: $u_i(c_i;E^*)=u_i(t_i,p_i)$. 


### Equivalent variation from the benchmark in the absence of transfers

To analyze an arbitrary situation $s$, it will be useful to relate it to two special cases. First, the coordinated situation $c*=(0,p^*)$, without transfer and with a uniform carbon price, which we take as a benchmark. Second, the autarchy situation $a=(0, p_i)$, without transfer and with differentiated prices, which will be a useful intermediary to analyze an arbitrary situation. We denote $V_i(p_i)$ the equivalent variation between situation $a$ and $c*$, i.e. the transfer required at $c*$ to get $a$'s welfare:
$$\begin{aligned}
u_i(V_i(p_i), p^*)&=u^a_i=u_i(0, p_i) \\
c^{c*}_i + V_i(p_i) &= c^a_i
\end{aligned}$$
In terms of welfare:
$$\begin{aligned}
u_i(V_i(p_i), p^*)&=u^a_i=u_i(0, p_i)=u_i(y_i-a_i(p_i))\sim u^{c*}_i - (p_i - p^*) \partial a_i \partial u_{i1} \\
u_i(V_i(p_i), p^*)&= u^{c*}_i + V_i(p_i)\partial u_{i1}
\end{aligned}$$
Therefore, 
$$V_i(p_i) = (p^* - p_i) \partial a_i$$

$V_i$ is positive iff $p^* > p_i$ as country i ``needs'' a positive compensation for consumption to get the same welfare as in (a) with a higher price $p^*$ (and lower emissions) compared to $c*$.

### Equivalent transfer for an arbitrary situation
Let $g^s_i$ be country $i$'s net gain (or ``equivalent transfer'') in an arbitrary situation $s=(t_i, p_i)$ compared to the benchmark situation $c*=(0,p^*)$: 
$$\begin{aligned}
g^s_i &= (c^s_i - c^a_i) + (c^a_i - c^{c*}_i) \\
 &= t_i + V_i(p_i)
\end{aligned}$$
Note that we can call $g^s_i$ the equivalent transfer as it is the transfer at zero price that makes $i$ indifferent with $s$, i.e. the transfer such that $(g^s_i, 0)$ is welfare-equivalent to $s=(t_i, p_i)$.


### Correspondence with an equivalent price

Now, we have all the tools to study the correspondence between transfers, differentiated emission rights, and differentiated prices. 
Let $p^*_i$ be the ``equivalent price'' such that $s=(t_i, p_i)$ is welfare-equivalent to $s*=(0, p^*_i)$. 
$$\begin{aligned}
g^s_i &= g^{s*}_i \\
t_i + V_i(p_i) &= V_i(p^*_i) \\
t_i + (p^* - p_i) \partial a_i &= (p^*- p^*_i) \partial a_i \\
\end{aligned}$$

Therefore, the equivalent price is:
$$p^*_i = p_i - \frac{t_i}{\partial a_i} $$

The equivalent price is negative when $p_i \partial a_i < t_i$. As a negative price would require a transfer from the rest of the world, a regime with differentiated (positive) prices is restrictive compared to a system that allows for international transfers. <!-- To implement transfers in the case where the equivalent price would be negative, -->
Therefore, we prefer to use the concept of equivalent transfer $g^s_i = t_i + (p^* - p_i) \partial a_i$.


### Correspondence between differentiated prices and rights

<!-- Denote $p$ the world average carbon price: $p=\sum_j p_j e_j n_j / E$, and $e$ the world average emission: $e=\sum_j e_j n_j / \sum_j n_j$.

Let us consider the case where countries pool their carbon price revenue: they collectively collect $\sum_j e_j p_j n_j = Ep$. -->
Imagine that countries establish a uniform carbon price $p^*$, e.g. through a cap-and-trade. Say each person in country $i$ has an emission right (or tradable budget) $b_i$, so they are entitled a claim $b_i p^*$ on global carbon revenue. Therefore, the net monetary transfer to $i$ is $$t^*_i = b_i p^* - e_i p^*$$

There is a correspondence between emission rights in a cap-and-trade and differentiated prices in autarchy (without transfers): 
$$\begin{aligned}
g^a_i &= V_i(p_i) = (p^* - p_i) \partial a_i \\
g^*_i &= t^*_i = (b_i - e_i) p^* \\
g^*_i = g^a_i &\Leftrightarrow b_i = e_i + (1 - \frac{p_i}{p^*}) \partial a_i  \\
&\Leftrightarrow p_i = p^* (1 + \frac{e_i - b_i}{\partial a_i})
\end{aligned}$$

TODO: estimate $\partial a_i$

<!--
Let us compare two special cases: a situation $d$ with differentiated prices but equal rights: $d=(ep-e_i p_i, p_i)$, and a situation $u$ with a uniform price but differentiated rights: $u=(b_i p^* - e_i p^*, p^*)$. We have:

$$\begin{aligned}
g^d_i &= ep - e_i p_i + V_i(p_i) \\
g^u_i &= b_i p^* - e_i p^*  \\
g^u_i - g^d_i &= b_i p^* - ep + (p_i - p^*) (e_i + \partial a_i) 
\end{aligned}$$
-->

### Using the status quo as benchmark

If, instead of using $c*=(0, p^*)$ as the counterfactual, governments use the status quo $c^- = (0, p^-)$, with $p^-<p^*$. Then, we the net gain they consider is 
$$\begin{aligned}
\gamma_i &= (y_i + t_i - a_i(p_i)) - (y_i - a_i(p^-)) + (E^* - E^-) \partial u_{i2}/\partial u_{i1} \\
 &= t_i -a_i(p_i) + a_i(p^-) + (E^* - E^-) \partial u_{i2}/\partial u_{i1} \\
 &\sim t_i + (p^- - p_i) \partial a_i + (p^* - p^-) \partial E \partial u_{i2}/\partial u_{i1} \\
 &= g_i - V_i(p^-) + (E^* - E^-) \partial u_{i2}/\partial u_{i1} \\
\end{aligned}$$ 
where $\partial u_{i3}$ corresponds to the welfare benefits of lower world emissions.

The gain relative to the status quo $\gamma_i$ is larger than the gain relative to $c*$ iff the price $p^*$ would improve welfare compared to the status quo price $p^-$, i.e. iff the welfare benefit from lower emissions exceeds the cost of decarbonization: 
$$\gamma_i > g_i \Leftrightarrow (E^* - E^-) \partial u_{i2}/\partial u_{i1} > V_i(p^-) $$


### Abatement cost required as transfer by those neglecting climate costs

From the point of view of short-sighted governments, we are likely in the other case $\gamma_i < g_i$, and these governments likely use $\gamma_i$ as a counterfactual to assess welfare. In the worst case where a government doesn't attach any value to a stable climate, accepting a price increase $\Delta p_i = p_i - p^-$ requires a transfer larger than the abatement costs:
$$t_i > \Delta p_i \partial a_i$$

Conceptually, abatement costs can be divided in two parts: first, the extra investments needed to build and deploy low-carbon infrastructure; second, the curtailment of consumption (of energy, meat, flights...) entailed by a higher carbon price. The former can be estimated with a bottom-up energy model, and the latter using the short (or medium) term price-elasticity of emissions $\epsilon = \frac{\partial e}{e}/\frac{\partial p}{p}$, and the crude approximation that emissions represent one-twentieth of the consumption (corresponding to half the energy share). Assuming $\epsilon = .4$, the effect on consumption of an increase in price by a factor $\delta p$ is therefore: $\delta c = \frac{\partial c/c}{\partial e/e} \epsilon \delta p = .05 \cdot .4 \cdot \delta p = .02 \cdot \delta p$. So, as a first approximation, a doubling of the carbon price should be compensated with a transfer of at least 2% of GDP.


## The dynamic case

### Setting

In this section, we will show that the correspondence between transfers and differentiated carbon prices imperfectly extends to the dynamic case. 

Let us keep the previous notations and add an index $t$ to denote the value of a variable at time $t$. Let $r_t$ be the discount factor between the initial period and $t$ (containing the pure rate of time preference and the welfare discounting from growth). Intertemporal values are denoted with uppercase letters. Monetary variables are discounted while physical ones are not, e.g. the intertemporal consumption of $i$ is $C_i = \sum_t c_{it} r_t$, its intertemporal net gain is $G_i = \sum_t g_{it} r_t$, and its intertemporal emission right is $B_i = \sum_t b_{it}$.

A situation $S$ is now given by the transfers and prices trajectories: $S=((t_{it})_t, (p_{it})_t)$. Taking $y_{it}$ as exogenous as a first approximation, a situation $S$ is welfare-equivalent to a situation $S'$ for country $i$ iff: $\sum_t t_{it} - a_{it}(p_{it}) = \sum_t t'_{it} - a_{it}(p'_{it})$.


### The uniform price without transfer case as benchmark

<!-- Consider the situation $C*$ of a global cap-and-trade system with a uniform carbon price. The transfers and price trajectories are determined by the allocation of the global intertemporal carbon budget $B$ at the country-by-period level: $(b_{it})_t$. -->
Consider the situation $C*=(0,(p^*_t)_t)$ of a uniform carbon price trajectory $(p^*_t)_t$ and within-country revenue recycling (i.e. without transfers). The carbon price trajectory may be fixed in advance or emerge from the temporal allocation of the global intertemporal carbon budget $B$ in a cap-and-trade system: $(b_{t})_t$. Let us define the net gain for $i$ at $t$ in a situation $S$ with the same emissions trajectory as $C*$ in relation to $C*$. As above: $g_{it} = t_{it} + V_{it}(p_{it})$, where $V_{it}(p_{it}) = (p^*_t - p_{it}) \partial a_{it}$.


### The difficulty to find a correspondence between differentiated prices and rights

As in the static case, let us look for a correspondence between an autarchy situation $A$ with differentiated prices and a cap-and-trade system $U$ with uniform price. In the general case, $A=(0, (p_{it})_t)$ while $U=(((b_{it}-e_{it})p^*_t)_t, (p^*_t)_t)$ is indirectly determined by $b=(b_{it})_t$. The welfare equivalence for $î$ between $A$ and $U$ requires:
$$\begin{aligned}
G^A_i &= \sum_t (p^*_t - p_{it}) \partial a_{it} r_t \\
G^U_i &= \sum_t (b_{it} - e_{it}) p^*_t r_t \\
G^U_i = G^A_i &\Leftrightarrow \sum_t b_{it} r_t p^*_t  = \sum_t (\partial a_{it} + e_{it}) p^*_t r_t - \sum_t p_{it} \partial a_{it} r_t  
\end{aligned}$$

Contrary to the static case, there is no direct equivalence between an intertemporal aggregate of the emission rights and an intertemporal aggregate of differentiated prices, since the welfare effect of emission rights depends on the cap-and-trade price trajectory $p^*_t$. 

The same reason also complicates the comparison between two possible allocations $b$ and $b'$ of the intertemporal carbon budget in a cap-and-trade, even when the price trajectory coincides. Indeed, the condition $G^U_i > G^{U'}_i \Leftrightarrow \sum_t b_{it} r_t p^*_t > \sum_t b'_{it} r_t p^*_t$ does *not* imply that $B_i = \sum_t b_{it} > \sum_t b'_{it} = B'_i$. In other words, there is no immediate relation between $i$'s intertemporal carbon budget and its intertemporal welfare, as the price trajectory matters.

Let us study whether we can find a correspondence in simpler cases. For the autarchy situation $A$, consider a homothetic carbon price vis-à-vis the world average: $p_{it}=\pi_ip_t$. For the cap-and-trade situation $U$, consider that $i$ is granted a fixed share of the world's carbon budget: $b_{it}=b_ib_t$. Now, the equivalence between $A$ and $U$ rewrites:

$$\begin{aligned}
G^U_i = G^A_i &\Leftrightarrow b_i \sum_t b_{t} r_t p^*_t  = \sum_t (\partial a_{it} + e_{it}) p^*_t r_t - \pi_i \sum_t p_{t} \partial a_{it} r_t  
\end{aligned}$$

Provided that the price trajectories in autarchy are homothetic to the price trajectory in the cap-and-trade, without loss of generality: $p_{it}=\pi_ip^*_t$; the equivalence simplifies further:

$$\begin{aligned}
G^U_i = G^A_i &\Leftrightarrow b_i \mathscr{B} = \mathscr{E} + (1 - \pi_i) \mathscr{\partial A}
\end{aligned}$$
where $\mathscr{B} = \sum_t b_{t} r_t p^*_t$, $\mathscr{E} = \sum_t e_{it} p^*_t r_t$, and $\mathscr{\partial A} = \sum_t \partial a_{it} p^*_t r_t$.

Although we do find a correspondence in this special case, the formula faces practical limitations, as it requires knowing the future price trajectory $(p^*_t)_t$, which can only be imprecisely estimated in the cap-and-trade situation. In any case, although one can find a trajectory of differentiated prices welfare equivalent to a given allocation of emissions rights, and vice versa, the derivation cannot be done analytically, one has to resort to an integrated assessment model. 

TODO: in the Hotelling case, the formula simplifies as $r_t p^*_t = p_0$.

```{r, echo=FALSE}



```
