---
title: "correspondence_price_rights"
output:
  html_document: default
  pdf_document: default
date: "2025-04-27"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

In case of global revenue use in proportion to $r_i$ of prices $p_i$, country's $i$ transfer $t_i$ is:
$$t_i = r_i p - e_i p_i$$

Denote $e^*_i(p_i)$ the emissions ``demand curve'': $e_i$ maximizing $u_i(c_i, e_i)$ s.t. $y_i = c_i + (p_e + \max\{0; p_i\}) e_i$.
For given world emissions $E$, define let $p^*$ be the price such that $\sum_i e^*_i(p^*) \cdot n_i = E$.
Let $g_i$ be country's $i$ net gain (or "equivalent transfer") in situation (transfers, prices) $j=(t_i, p_i)$ compared to the situation $c*=(0, p^*)$ in terms of equivalent variation. Define $V_i(p_i)$ the equivalent variation between situation $a=(0, p_i)$ and $c*$ (i.e. the compensation at $c*$ needed to get $a$'s utility:
$$g_i = (y^j_i - y^a_i) + (y^a_i - y^{c*}_i) = t_i + V_i(p_i)$$
$$\begin{aligned}
u^a_i &= u_i(c_i, e^*_i(p_i)) = u^{c*}_i + (p_i - p^*) \partial u_{i2} \partial e^*_i  \\
u^{c*}_i &= u_i(c_i, e^*_i(p^*)) \\
u^a_i &= u_i(c_i + V_i(p_i), e^*_i(p^*))= u^{c*}_i + V_i(p_i) \partial u_{i1}
\end{aligned}$$

Therefore
$$V_i(p_i) = -(p^* - p_i) \partial u_{i2} \partial e^*_i / \partial u_{i1}$$

$V_i$ is positive iff $p^* > p_i$ as country i "needs" a positive compensation for consumption to get the same utility as in (a) with a higher price $p^*$ / lower emissions in ($c*$).

Comparing situation (d) with differentiated prices but equal rights: $d=(ep^* - e_i p_i, p_i)$ with 
situation (u) with a uniform price but differentiated rights: $u=(r_i p^* - e_i p^*, p^*)$, we have:

$$\begin{aligned}
g^d_i &= ep^* - e_i p_i + V_i(p_i) \\
g^u_i &= r_i p^* - e_i p^*  \\
g^u_i - g^d_i &= (r_i - e) p^* + (p_i - p^*) e_i - V_i(p_i) = (r_i - e) p^* + (p_i - p^*) \cdot (e_i - \partial u_{i2} \partial e^*_i / \partial u_{i1})
\end{aligned}$$

Let $\pi^j_i$ the "equivalent price" such that $j=(t_i, p_i)$ is utility-equivalent to $j*=(0, \pi^j_i)$. 
$$\begin{aligned}
u^j_i &= u^{j*}_i \\
u^{j*}_i &= u_i(c_i, e^*_i(\pi_i)) \\
u^j_i &= u_i(c_i + t_i, e^*_i(p_i))  = u^{j*}_i + t_i \partial u{i1} + (p_i - \pi_i) \partial u_{i2} \partial e^*_i
\end{aligned}$$

Therefore, the equivalent price is:
$$\pi_i = p_i - \frac{t_i \partial u{i1}}{-\partial u_{i2} \partial e^*_i(\pi_i)} $$
The equivalent price is ill-defined in case it is negative in the above formula. Hence, when $p_i/t_i < \frac{t_i \partial u{i1}}{-\partial u_{i2} \partial e^*_i(\pi_i)}$, we instead use the notion of "equivalent transfer at zero price": $t^{0*}_i$ such that $(t^{0*}_i, 0)$ (with $\pi_i = 0$) is utility-equivalent to $j=(t_i, p_i)$.
$$\begin{aligned}
u^j_i &= u^{0*}_i \\
u^{0*}_i &= u_i(c_i + t^{0*}_i, e^*_i(0)) \\
u^j_i &= u_i(c_i + t_i, e^*_i(p_i))  = u^{0*}_i + (t_i - t^{0*}_i) \partial u{i1} + p_i \partial u_{i2} \partial e^*_i \\
\Rightarrow t^{0*}_i &= t_i - p_i \frac{-\partial u_{i2} \partial e^*_i(0)}{\partial u{i1}}
\end{aligned}$$

Now, let us study the situation (n) with differentiated prices and no international transfers. We simply have 
$$g_i = V_i(p_i) = -(p^* - p_i) \partial u_{i2} \partial e^*_i / \partial u_{i1}$$

If, instead of using $c*=(0, p^*)$ as the counterfactual, we used the status quo $c^- = (0, p^-)$, with $p^-<p^*$. Then, we redefine the net gain as 
$$g^-_i = y^j_i - y^{c^-}_i = t_i + V_i(p_i) + y^{c*}_i - y^{c^-}_i = g_i + (p^* - p^-) (\partial u_{i3} + \partial u_{i2} \partial e^*_i / \partial u_{i1}) = t_i - (p^- - p_i)\partial u_{i2} \partial e^*_i / \partial u_{i1} + (p^* - p^-) \partial u_{i3} $$ 
where $\partial u_{i3}$ corresponds to the climate benefits of a higher carbon price.

Therefore, the gain relative to the status quo $c^-$ is higher than the gain relative to $c*$ iff the price $p^*$ would improve welfare compared to the status quo price $p^-$, i.e. iff the climate benefit from a higher price $p^*$ exceeds the cost of decarbonization: 
$$g^-_i > g_i \Leftrightarrow \partial u_{i3} > -\partial u_{i2} \partial e^*_i / \partial u_{i1}$$
From the point of vue of short-sighted (LIC) governments, we are likely in the other case $g^-_i < g_i$, and these governments likely use $g^-_i$ as a counterfactual to assess welfare. In the worst case where a government doesn't attach any value to less global warming, to accept a price increase $\Delta p_i$, it requires a transfer 
$$t_i > -\Delta p_i \partial u_{i2} \partial e^*_i / \partial u_{i1} =: t^-_i$$

I am not sure of the first equation below, which comes from comparing the semi-elasticities of utility to consumption and emissions (assuming the former is 10 times larger). 
$$c\partial u_1 = 10 \cdot e \partial u_2 \Rightarrow \partial e \partial u_2 / \partial u_1 = -\epsilon \cdot c/(p\cdot 10) \Rightarrow t^-_i = \epsilon \cdot \Delta p_i/p_i \cdot c_i / 10 $$
where $\epsilon \approx .5$ is the absolute price elasticity of emissions and 10 is the likely ratio between overall consumption and energy/emissions-related consumption. So, as a first approximation a doubling of the carbon price should be associated with a transfer of at least 5% of GDP.

```{r, echo=FALSE}



```

